---
title: "MER Quality Assessment Template"
format: html
editor: 
  markdown: 
    wrap: 72
---

::: {#motivation}
# MOTIVATION
:::

From Gebru et al. (2019)

**For what purpose was the dataset created?** Was there a specific task
in mind? Was there a specific gap that needed to be filled? Please
provide a description.

```{r echo = FALSE}
shiny::textInput('Q1', "Answer here:")
```

**Who created this dataset (e.g., which team, research group) and on
behalf of which entity (e.g., company, institution, organization)?**\

```{r echo = FALSE}
shiny::textInput('Q2', "Answer here:")
```

**What support was needed to make this dataset?** (e.g. who funded the
creation of the dataset? If there is an associated grant, provide the
name of the grantor and the grant name and number, or if it was
supported by a company or government agency, give those details.)\

```{r echo = FALSE}
shiny::textInput('Q3', "Answer here:")
```

Adapted from Wang & Strong (1996,7)

::: {#intrinsic}
# INTRINSIC DQ
:::

**The task draws from relevant theories.** Does the task draw from
prevailing theories of emotion? Are any compromises made, or
inconsistencies introduced, when adapting theory for the research task?

```{r echo = FALSE}
shiny::textInput('Q4', "Answer here:")
shiny::selectInput('R4', 'Rating', 1:5)
```

**Analyses were conducted to assess the reliability of results.** Were
additional analyses performed for validation (e.g., interrater
reliability, cross-validation?) Do decisions give the impression these
results are generalizable?

```{r echo = FALSE}
shiny::textInput('Q5', "Answer here:")
shiny::selectInput('R5', 'Rating', 1:5)
```

**Study design decisions provide an impression that the study results
are believable and replicable.** Does the combination of decisions about
the measurement construct; participant recruitment; stimulus, feature,
and model selection lead to an impression that the study conclusions are
appropriate and believable?

```{r echo = FALSE}
shiny::textInput('Q6', "Answer here:")
shiny::selectInput('R6', 'Rating', 1:5)
```

**The study appears to be reputable when considering the journal and
readership/citation metrics.**

```{r echo = FALSE}
shiny::textInput('Q7', "Answer here:")
shiny::selectInput('R7', 'Rating', 1:5)
```

::: {#accessibility}
# ACCESSIBILITY DQ
:::

**The data from this project are publicly available.** Do any barriers
exist that could impact the reproducibility of the project? (e.g.,
copyright issues, lack of documentation, poor repository management).

```{r echo = FALSE}
shiny::textInput('Q8', "Answer here:")
shiny::selectInput('R8', 'Rating', 1:5)
```

From Gebru et al. (2019)

**The dataset is self-contained, or links to otherwise external
resources (e.g., websites, tweets, other datasets).** If it links to or
relies on external resources, a) are there guarantees that they will
exist, and remain constant, over time; b) are there official archival
versions of the complete dataset (i.e., including the external resources
as they existed at the time the dataset was created); c) are there any
restrictions (e.g., licenses, fees) associated with any of the external
resources that might apply to a future user?

```{r echo = FALSE}
shiny::textInput('Q9', "Answer here:")
shiny::selectInput('R9', 'Rating', 1:5)
```

**Do users require special permissions to access the data?** Are costs
associated with the creation of the dataset reported?

```{r echo = FALSE}
shiny::textInput('Q10', "Answer here:")
shiny::selectInput('R10', 'Rating', 1:5)
```

::: {#contextual}
## CONTEXTUAL DQ
:::

From Gebru et al. (2019)

**Does the dataset contain all possible instances or is it a sample (not
necessarily random) of instances from a larger set?** If the dataset is
a sample, then what is the larger set? Is the sample representative of
the larger set (e.g., geographic coverage)? If so, please describe how
this representativeness was validated/verified. If it is not
representative of the larger set, please describe why not (e.g., to
cover a more diverse range of instances, because instances were withheld
or unavailable).

```{r echo = FALSE}
shiny::textInput('Q11', "Answer here:")
shiny::selectInput('R11', 'Rating', 1:5)
```

**If the dataset is a sample from a larger set, what was the sampling
strategy (e.g., deterministic, probabilistic with specific sampling
probabilities)?**

```{r echo = FALSE}
shiny::textInput('Q12', "Answer here:")
shiny::selectInput('R12', 'Rating', 1:5)
```

**The dataset reflects functional open data practices.** How easily
accessible is the dataset to new users?

```{r echo = FALSE}
shiny::textInput('Q13', "Answer here:")
shiny::selectInput('R13', 'Rating', 1:5)
```

**The dataset fills a gap in the literature.**

```{r echo = FALSE}
shiny::textInput('Q14', "Answer here:")
shiny::selectInput('R14', 'Rating', 1:5)
```

**Is the public-facing dataset available in partial or complete form?**
In other words, is enough data provided that the analyses reported in
the accompanying paper can be reproduced?

```{r echo = FALSE}
shiny::textInput('Q15', "Answer here:")
shiny::selectInput('R15', 'Rating', 1:5)
```

**How many observations of each type of instance are available?** e.g.,
stimuli, participants, annotations.

```{r echo = FALSE}
shiny::textInput('Q16', "Answer here:")
shiny::selectInput('R16', 'Rating', 1:5)
```

::: {#representation}
## REPRESENTATIONAL DQ
:::

**The dataset documentation is complete and clearly understandable.** Is
sufficient information provided to understand how data are stored (e.g.,
repository structure and filenames), represented (column names, data,
and metadata), and analyzed (preprocessing/analysis scripts)?

```{r echo = FALSE}
shiny::textInput('Q17', "Answer here:")
shiny::selectInput('R17', 'Rating', 1:5)
```

**The data are represented concisely.** Are data provided in a
human-readable format? Are redundant observations, verbose labels, or
missing values/outliers accounted for in preprocessing and/or
documentation?

```{r echo = FALSE}
shiny::textInput('Q18', "Answer here:")
shiny::selectInput('R18', 'Rating', 1:5)
```

**Measured constructs are represented and applied in a manner that is
both internally consistent within the study, and externally consistent
with other studies.** In other words, are frameworks employed
consistently employed throughout the study, as well as with other
studies in the literature?

```{r echo = FALSE}
shiny::textInput('Q19', "Answer here:")
shiny::selectInput('R19', 'Rating', 1:5)
```

**What demographic/level of expertise do the annotators represent?**
Does the design of study account for differences in expertise, primary
language, demographics? If so, is this information available to users of
the dataset?

```{r echo = FALSE}
shiny::textInput('Q20', "Answer here:")
shiny::selectInput('R20', 'Rating', 1:5)
```
